\documentclass{article}

\title{Example of revisions}
\author{Giuseppe Lipari\\\texttt{giuseppe.lipari@univ-lille1.fr}}
\def\RevVersion{}
\input{rev-macros}

\begin{document}

\maketitle

\section{Introduction}

This is a simple example of use of the revision
macros defined in \texttt{rev-macros.tex}. We want to delete this sentence.

Of course, there are several ways to use this. There is the
possibility to corrects typing errors; and also to add
additional text later on; 

Substitute is useful when we want to delete and add at the same
time. We want to substitute this long and boring piece of
  text that does not say anything interesting and may be safely
  substitute with this shorter text.

Notice that there is the possibility to show the revisions,  to show the
old text,  or just show the new
version .

Finally, at some point the tex file usually becomes cluttered with
added, substituted, deleted macros, and so it is difficult to be
read. In that case, you can eliminate all macros by running the
 script \texttt{accept\_revisions.py} passing the file
as first argument. The script will search all every use of the macro
in the file and propose you three choices: (a)ccept , (r)eject  and (s)kip
. 
The output is recorded in a
different file with the same name extended with \texttt{\_new.tex}.


It also takes three possible options:

\begin{itemize}
\item \texttt{-h, --help} print the help 

\item \texttt{-a, --accept} accept all changes
  (non-interactive) 
\item \texttt{-r, --reject} reject all changes (non-interactive)
\end{itemize}
The changes are written on a \texttt{/tmp/accept-temp} file and
recopied on the original file before the script ends. If you press
\texttt{Ctrl-C} before the script ends, the original file is not
overwritten and the partial changes remain in
\texttt{/tmp/accept-temp}.

Enjoy it! 



\end{document}

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: t
%%% End: 
